---
title: "Final Project"
author: "Yifei Lin"
date: "February 17, 2017"
output: html_document
---
 
## Step 1: Download Data
```{r}
if(!file.exists("./data")) {dir.create("./data")}
fileurl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
download.file(fileurl,destfile = "./data/final.zip",method = "curl")
unzip(zipfile = "./data/final.zip",exdir = "./data")
```

## Step 2: Check all data
```{r}
list.files("./data")
all_file <- list.files("./data/UCI HAR Dataset",recursive = T)
file_use <- all_file[c(1,2,3,14,15,16,26,27,28)]
file_use
```

## Step 3: Read Data
```{r}
x_test <- read.table("./data/UCI HAR Dataset/test/X_test.txt",header = F)
x_train <- read.table("./data/UCI HAR Dataset/train/X_train.txt",header = F)

y_test <- read.table("./data/UCI HAR Dataset/test/y_test.txt",header = F)
y_train <- read.table("./data/UCI HAR Dataset/train/y_train.txt",header = F)

sub_test <- read.table("./data/UCI HAR Dataset/test/subject_test.txt",header = F)
sub_train <- read.table("./data/UCI HAR Dataset/train/subject_train.txt",header = F)

name <- read.table("./data/UCI HAR Dataset/features.txt",header = F)
```

## Step 4: Merges the training and the test sets to create one data set
```{r}
x <- rbind(x_train,x_test)
#head(x,1);ncol(x)
y <- rbind(y_train,y_test)
#head(y)
subject <- rbind(sub_train,sub_test)
#head(subject)

names(y)<-"Activity"
names(subject)<-"Subject"
names(x)<-name$V2

final_data <- cbind(subject,y,x)
```

## Step 5: Extracts only the measurements on the mean and standard deviation for each measurement
```{r}
columns <- grep("mean\\(\\)|std\\(\\)",names(final_data))
mean_std_data <- final_data[,c(1,2,columns)]
dim(mean_std_data)
```

## Step 6: Uses descriptive activity names to name the activities in the data set
```{r}
act_label <- read.table("./data/UCI HAR Dataset/activity_labels.txt",header = F)
for(i in 1:nrow(final_data)) {
  final_data$Activity[i]<-as.character(act_label$V2[final_data$Activity[i]==act_label$V1])
}
```

## Step 7:Appropriately labels the data set with descriptive variable names
```{r}
names(final_data)<-gsub("^t", "time", names(final_data))
names(final_data)<-gsub("^f", "frequency", names(final_data))
names(final_data)<-gsub("Acc", "Accelerometer", names(final_data))
names(final_data)<-gsub("Gyro", "Gyroscope", names(final_data))
names(final_data)<-gsub("Mag", "Magnitude", names(final_data))
names(final_data)<-gsub("BodyBody", "Body", names(final_data))
```

## Step 8: creates a second, independent tidy data set with the average of each variable for each activity and each subject.
```{r}
if (!require("plyr")) install.packages('plyr')
library(plyr)
second_tidy<-aggregate(. ~Subject + Activity, final_data, mean)
```


